Welcome to the 2025 Widening NLP Workshop!

\vspace{\baselineskip}

The origins of this workshop trace back to ACL 2016 in Berlin, where a small group gathered to address the underrepresentation of women and other minorities in the Natural Language Processing (NLP) community. That conversation led to the inaugural Workshop for Women and Underrepresented Minorities in NLP at ACL 2017—a dedicated space to highlight the voices and contributions that are too often overlooked. Since then, Widening NLP has continued to grow, and we are proud to carry this important tradition forward in 2025.

\vspace{\baselineskip}

Over the years, we have taken deliberate steps to make the workshop more inclusive. Following the inaugural 2017 event, we introduced two submission deadlines—an early one to support those requiring additional time for visa applications and a later one for others without such constraints. Building on the success of 2018, the 2019 edition expanded our focus to celebrate diversity not only in gender and minority identity but also in scientific background, discipline, degree, training, and seniority. That year, we also launched a peer feedback system, giving authors the chance to receive constructive input from colleagues prior to formal review. 

\vspace{\baselineskip}

The global pandemic brought new challenges by canceling in-person events, yet it also created opportunities to broaden access. Since 2021, we have embraced a hybrid format that enables us to welcome a wider audience while continuing to support in-person participation. In addition, we repurposed travel funds to cover high-speed internet and registration costs, ensuring that even more participants could engage in the virtual workshop.

\vspace{\baselineskip}

This year, we are excited to present a truly outstanding program. From 76 submissions, 41 papers were accepted, reflecting both the quality and diversity of perspectives within our community. We are honored to feature two distinguished invited speakers - Jen-Tse Huang and David Adelani, as well as four excellent panelists - Christos Christodoulopoulos, Julia Kreutzer, Pittawat Taveekitworachai, Zhisong Zhang. Their talks and discussions will inspire us with the wealth of talent and ideas driving the advancement of NLP today.

\vspace{\baselineskip}

We warmly welcome you to the 2025 Widening NLP Workshop. We hope you will find inspiration in the work of our authors, speakers, and panelists, and that this gathering will continue to foster new connections, collaborations, and possibilities for an ever more inclusive NLP community.

\vspace{\baselineskip}

-Chen, Emily, Hua, Lesly, Yinqiao, Meryem, Peerat, Richard, Santosh, Sophia, Surendrabikram, Wiem, Organizing Co-Chairs