

\textbf{Christos Christodoulopoulos}

Christos Christodoulopoulos is a Principal Technology Adviser in the AI Policy \& Compliance teams of the Information Commissioner's Office, UK’s Data Protection regulator. Before joining the ICO, he was an Applied Scientist at Amazon, starting in 2016 on the Alexa AI Knowledge team and ending as a Senior Applied Scientist at Amazon's Responsible AI team working on multimodal and agentic FM development. Before Amazon, he was a postdoctoral researcher at UIUC working with Dan Roth on Semantic Role Labeling and Cindy Fisher on computational models of child language acquisition. He has an MSc and PhD from the University of Edinburgh. He is a Program Chair for EMNLP 2025, an organiser for the FEVER, GenBench, and TrustNLP workshops and has served as a reviewer, area chair and senior area chair for many *CL conferences.

\vspace{\baselineskip}

\textbf{Julia Kreutzer}

Julia Kreutzer is a Senior Research Scientist at Cohere Labs, where she conducts research on large language models, currently focused on multilinguality, evaluation and inference. Previously, she worked at Google Translate, and completed her PhD at Heidelberg University on learning from human feedback in machine translation. She's been an active contributor to multiple open-science communities and a co-organizer of COLM, WMT shared tasks and various NLP workshops.

\vspace{\baselineskip}

\textbf{Pittawat Taveekitworachai}

Pittawat (Pete) Taveekitworachai is a research scientist on the Typhoon team at SCB 10X in Thailand. His research interests include reasoning models, test-time scaling, prompt engineering, and reinforcement learning. He completed his Master’s degree (as valedictorian) at Ritsumeikan University, Japan, under the Japanese Government Scholarship (MEXT), where his research focused on prompt engineering, large language models, and their applications in gaming, healthcare, and autonomous driving. At SCB 10X, he leads research collaborations with academic and industry partners, both domestically and internationally. He is passionate about translating cutting-edge research into real-world applications and values both the scientific rigor and engineering practicality that drive impactful innovation.

\vspace{\baselineskip}

\textbf{Zhisong Zhang}

Zhisong Zhang is currently an Assistant Professor in the Department of Computer Science of City University of Hong Kong. He holds a PhD from the Language Technologies Institute at Carnegie Mellon University. His doctoral research focused on advancing natural language processing (NLP) systems, particularly in data-limited scenarios, where his work aimed to reduce the need for labor-intensive manual data labeling while improving task performance. After PhD graduation, he had also worked as a researcher in Tencent before joining CityUHK. His current research focuses on natural language processing (NLP) and large language models (LLMs), with particular interests in long-context language modeling, LLM-based agent systems, and understanding the underlying mechanisms of language models. Please refer to his homepage for more details: https://zzsfornlp.github.io/
